\documentclass[11pt]{article}
\usepackage{url}
\usepackage{tikz}
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0in
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in

\begin{document}
\pagenumbering{gobble}
\centerline{{\Huge \sc Giovanni DeGrande}}
\centerline{177 Bennett Rd \textbullet \hspace{5pt} Freehold, NJ 07728 \textbullet \hspace{5pt} (732)-598-5774}
\centerline{degrangi@gmail.com}
\centerline{\url{https://github.com/Degrangio}}
\noindent
\line(1,0){470}

\newcommand{\Objective}
{
    \noindent{\Large \bf Objective}
    \smallskip
    \noindent Create new and innovative technologies by leveraging strong soft skills and coding expertise. \medskip
}

\newcommand{\ExecutiveSummary}
{

    \noindent{\Large \bf Executive Summary}
    
    
    \noindent{Experience in ballistic missile defence with an emphasis on coordinating weapon and sensor data in a high performance, time critical, and fault tolerant environment. Thrives in an agile team environment that encourages initiative and rapid development.}

    \medskip
    \noindent Developed utilities and products in the following languages:
  
    \centerline{\hfill $\bullet$ C++ \hfill $\bullet$ Python \hfill $\bullet$ Java \hfill $\bullet$ C \hfill $\bullet$ C\# \hfill $\bullet$ Bash \hfill $\bullet$ Javascript \hfill}
    \medskip
    \noindent Proficient with the following tools:

    \centerline{
    \hfill $\bullet$ Docker \hfill $\bullet$ Blue Ocean \hfill $\bullet$ Kubernetes \hfill $\bullet$ Angular2 \hfill $\bullet$ Express \hfill $\bullet$ MySQL \hfill $\bullet$ Node \hfill $\bullet$ Artifactory \hfill $\bullet$ JSON \hfill $\bullet$ LaTeX
    }
    \centerline{
      \hfill $\bullet$ Jenkins \hfill $\bullet$ MongoDB \hfill $\bullet$ Git \hfill $\bullet$ Clearcase \hfill $\bullet$ Jira \hfill $\bullet$ Vim \hfill $\bullet$ Eclipse \hfill $\bullet$ Visual Studio \hfill $\bullet$ Gdb
    }
    \centerline{
      \hfill $\bullet$ Ibm Doors \hfill $\bullet$ Rhapsody \hfill $\bullet$ Virtual Box \hfill $\bullet$ Linux \hfill $\bullet$ XML
    }
}

\newcommand{\Education}
{
    \noindent{\Large \bf Education}

    \smallskip
    \noindent \centerline{Rutgers University, School of Engineering \hfill2015}

    \smallskip
    \indent{$\bullet$ \textit{B.S. Electrical and Computer Engineering}}
}

\newcommand{\NewJobTitle}[2]
{
  \begin{flushleft}
	#1
	\hfill #2 \hfill
  \end{flushleft}
}

\newcommand{\JobBullet}[1]
{
    \begin{itemize}
	\item #1
    \end{itemize}
}

%\Objective
\smallskip

\ExecutiveSummary
\bigskip

\Education
\bigskip

\noindent{\Large \bf Professional Experience}
\NewJobTitle{ASRC Federal Mission Solutions Engineering}{June 2015 - Present}
\JobBullet{Implemented a pipeline as a model for the company transition to Software factories including the development of Docker images for building code, running static analysis and deploying code to test machines for automatic Regression Testing.} 
\JobBullet{Mentored numerous Junior Developers on automated testing and Software Development cycle.}
\JobBullet{Helped customers navigate new contract demands of DevOps by supplying the customer with an architecture to deliver third party code utilizing artifactory.}
\JobBullet{Worked closely with Lockheed Martin Engineers as part of the software developement life cycle to generate Models, Code, Test Procedures, Unit Test, and automated integration tests in a variety of languages.}
\JobBullet{Led initiative on creating level 2 drivers in Python and Java for the move to continuous integration and DevOps.}
\JobBullet{Utilized Python Gtk and Bash to bind the different company tools for automated generation of code metrics and review materials.  This tool has been adopted across multiple departments and has improved the productivity of all employees who use it.}
\JobBullet{Developed a virtual reality weapon console using Unity, the Occulus Rift, and the Leapmotion VR as part of a code-athon effort. The code developed from this effort has generated support for the pursuit of new contracts.}


\NewJobTitle{Aviv Biomedical Inc.}{May 2013 - June 2015}
\JobBullet{Used Eagle Pcb and Codewarrior Developement environment to create embedded systems and software for photoluminescence spectrometers.}
\JobBullet{Programmed freescale microcontrollers in C to operating mechanical arms and gather data from photomultiplier tubes for the purpose of sample analysis.}
\JobBullet{Created GUI applications utilizing Winforms, MFC, and WPF to operate embedded systems and visualize data.}

\centerline{\textbf{Active Security Clearance}}

\end{document}
